 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-04-17 paper.Rmd
add citations

Taken together, these details reveal the sheer number of decisions that an 
anlayst must make. How does one choose the perplexity? How should the parameters
that control the optimisation of the loss function (done with stochastic
gradient descent), like the number of iterations, or early exaggeration (
a multiplier of the attractive force at the beginning of the optimisation),
or the learning rate be selected?  It is a known
problem that t-SNE can have trouble recovering topology and that
configurations can be highly dependent on how the algorithm is initialised and
parameterized [@Wattenberg2016-ji; @Kobak2019-lm]. If the goal is cluster
orientation a recent theoretical contribution by @Linderman2019-dq proved
that t-SNE can recover spherical and well separated cluster shapes, and
proposed new approaches for tuning the optimisation parameters. However,
the cluster sizes and their relative orientation from a $t-SNE$ view can be 
misleading perceptually, due to the algorithms emphasis on locality.

>>>>

Taken together, these details reveal the sheer number of decisions that an 
anlayst must make. How does one choose the perplexity? How should the parameters
that control the optimisation of the loss function (done with stochastic
gradient descent), like the number of iterations, or early exaggeration (
a multiplier of the attractive force at the beginning of the optimisation),
or the learning rate be selected?  It is a known
problem that t-SNE can have trouble recovering topology and that
configurations can be highly dependent on how the algorithm is initialised and
parameterized [@Wattenberg2016-ji; @Kobak2019-lm; @Melville2020]. If the goal is
cluster orientation a recent theoretical contribution by @Linderman2019-dq proved
that t-SNE can recover spherical and well separated cluster shapes, and
proposed new approaches for tuning the optimisation parameters. However,
the cluster sizes and their relative orientation from a $t-SNE$ view can be 
misleading perceptually, due to the algorithms emphasis on locality.
